Twists of supersymmetric gauge theories

### 2019-05-31 paper.tex
Editing section 10

\begin{dfn}
A {\bf free classical field theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ$-graded vector bundle $E \to M$ equipped with a differential operator of cohomological degree $+1$
\[
Q : \cE \to \cE [1] 
\]
such that (1) $Q^2 = 0$ and (2) $(\cE , Q)$ is an elliptic complex;
\item a map of bundles
\[
\omega : E \otimes E \to {\rm Dens}_M [-1]
\]
that is (1) fiberwise nondegenerate, (2) graded skew symmetric, and (3) satisfies $\int_M \omega\<e_0, Qe_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{itemize}
\end{dfn}

@@

Now, to verify that this morphism is an equivalence as in Definition \ref{equivalence_def}, we must check that the induced morphism 
\[\iota^* \colon  \left(\cO(\cE_{\mr{SYM}})[-1], Q_{\mr{SYM}} + \{I_{\mr{BV}} + I^{(1)}_Q,-\} \right) \xto{\simeq} \left(\cO(\cE_\hCS)[-1], Q_\hCS + \{I_\hCS,-\} \right)\]
is a quasi-isomorphism. \chris{...}

>>>>

\begin{dfn}
A {\bf free classical field theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ$-graded vector bundle $E \to M$ equipped with a differential operator of cohomological degree $+1$
\[
Q \colon \cE \to \cE [1] 
\]
such that (1) $Q^2 = 0$ and (2) $(\cE , Q)$ is an elliptic complex;
\item a map of bundles
\[
\omega : E \otimes E \to {\rm Dens}_M [-1]
\]
that is (1) fiberwise nondegenerate, (2) graded skew symmetric, and (3) satisfies $\int_M \omega\<e_0, Qe_1\> = (-1)^{|e_0|} \int_M \omega(Q e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{itemize}
\end{dfn}

@@

Now, to verify that this morphism is an equivalence as in Definition \ref{equivalence_def}, we must check that the induced morphism 
\[\iota^* \colon  \left(\cO(\cE_{\mr{SYM}})[-1], Q_{\mr{SYM}} + \{I_{\mr{BV}} + I^{(1)}_Q + I^{(2)}_{Q\otimes Q},-\} \right) \xto{\simeq} \left(\cO(\cE_\hCS)[-1], Q_\hCS + \{I_\hCS,-\} \right)\]
is a quasi-isomorphism. \chris{maybe try filtering the left-hand side by the number of $\chi$ and $\chi^\vee$ fields occuring.  The 0th filtered piece should coincide with the right-hand side exactly, and maybe we'd like to see that everything else is killed off by some differential in the spectral sequence?}
